Circularity in Population-Based FA Analysis

### 2011-06-25 ANTsTBSS/paper.tex
Added a single reference.

The seminal work of Basser et al. \citep{Basser1994a,Basser1994} established diffusion tensor imaging (DTI) as a viable investigatory MRI technique.  DTI's sensitivity to brain architecture \citep{Basser1996,Assaf2008} enables promising analysis possibilities assessing neuro-structural differences in cross-population studies \citep{Kubicki2005,Arnone2008,Kantarci2010,Rametti2010} including subjects with traumatic brain injury (TBI) \citep{Caeyenberghs2010,Jiang2010,Warner2010}.  Two popular comprehensive software packages for assessing population FA differences include the SPM Matlab-based toolkit%
\footnote{
http://www.fil.ion.ucl.ac.uk/spm/
}
for voxel-based morphometry (VBM)
and the tract-based spatial statistics (TBSS) framework \citep{Smith2006}.%
\footnote{
http://www.fmrib.ox.ac.uk/fsl/tbss/index.html
} 
VBM \citep{Ashburner2001} continues to find application to FA studies \citep{Kakeda2010,Takao2010} despite concerns about its general validity \citep{Bookstein2001,Davatzikos2004} and with respect to DTI \citep{Jones2005,Chung2008}.  The TBSS framework was partially developed in response to these concerns in which voxel values are projected onto a template white matter skeleton for increased statistical power.  
%(e.g. \citep{Arnone2008,Bodini2009}).

>>>>

The seminal work of Basser et al. \citep{Basser1994a,Basser1994} established diffusion tensor imaging (DTI) as a viable investigatory MRI technique.  DTI's sensitivity to brain architecture \citep{Basser1996,Assaf2008} enables promising analysis possibilities assessing neuro-structural differences in cross-population studies \citep{Kubicki2005,Arnone2008,Kantarci2010,Rametti2010} including subjects with traumatic brain injury (TBI) \citep{Caeyenberghs2010,Jiang2010,Warner2010}.  Two popular comprehensive software packages for assessing population FA differences include the SPM Matlab-based toolkit%
\footnote{
http://www.fil.ion.ucl.ac.uk/spm/
}
for voxel-based morphometry (VBM)
and the tract-based spatial statistics (TBSS) framework \citep{Smith2006}.%
\footnote{
http://www.fmrib.ox.ac.uk/fsl/tbss/index.html
} 
VBM \citep{Ashburner2001} continues to find application to FA studies \citep{Kakeda2010,Takao2010,Preziosa2011} despite concerns about its general validity \citep{Bookstein2001,Davatzikos2004} and with respect to DTI \citep{Jones2005,Chung2008}.  The TBSS framework was partially developed in response to these concerns in which voxel values are projected onto a template white matter skeleton for increased statistical power.  
%(e.g. \citep{Arnone2008,Bodini2009}).
